\documentclass{article}
\title{Keyword project Entry 6}
\author{Mackenzie Norman}
\begin{document}
\maketitle 
The requirement of the blowjob in TLATOMK

I was shocked (as I think everyone was) by the sexual assault at the end of The Life and Times of Micheal K. There is a lot to say about this, but from a body perspective, the first thing I thought when reading this was along the lines of `Wow - the whole time K. has been described as sexless and stated he wasn't even interested in women. this seems like a big change' 

I think K. being forced to ejaculate is important, From O. Brown ``The blood or the soul is the seminal fluid. The fission, or self-alienation which produces this abstract substance, separate from the body but the life of it, is ejaculation. Ejaculation is fission'' We can read his ejaculation as fission, the soul leaving the body, death even. The question this raises is was there a soul to leave the body of K. Contrasting mind and body, K. gives us a fascinating look

``In oral copulation the vagina is a devouring mouth.
 The combined object (parents in coitus) becomes the
 mother with a penis. The father is castrated; the mother
 retains his penis. "The horrible woman who thrusts her
 long nose into the room through the window at night
 to alarm the cobbler is clearly the dream apparition of
 the old woman with a penis, that is the primal scene in
 the abbreviated form of the combined parent.''

 ``Oral copulation, or the equation of penis and breast,
 the crux in sexual inversion. Coitus as castration. To be
 castrated is to be a woman; but the woman is a devouring
 mouth which castrates. Those who have been castrated
 must castrate others to incorporate their penis; but to receive into themselves a penis is again to be a woman, to
 be castrated. The solution to the castration-complex is
 genital organization. But genital organization is the basic
 equation of body (self) and penis; and "the sexual aim
 of a person who has in phantasy eaten the penis and be
come the penis is—to be eaten."''
``The woman gave me and
 I did eat. Eating is the form of sex. Copulation is oral
 copulation; when the Aranda ask each other, "Have you
 eaten?" they mean, "Have you had intercourse?" The
 schizophrenic girl refused to eat; the case of Simone Weil.
 Eating is the form of war. Human blood is the life and de
lightful food of the warrior. Eating is the form of redemp
tion. Except ye eat the flesh of the Son of man, and drink
 his blood, ye have no life in you. We must eat again of the
 tree of knowledge, in order to fall into innocence.''
\end{document}