\textit{``The question what is a body, is the question what is it to eat: Take, eat; this is my body.''}(Brown) 


When I think of body in terms of colonialism I first think of the human body, and the legislation and control often exerted on bodies by colonial powers. In a literary sense, I thought of Quentin Compsons obession with the purity of his sisters body in \textit{The Sound and The Fury} which you can read as colonialism (is the old confederate south not a bastion of colonialism) being one of the multitude of anachronisms that tear Quentin apart. I chose body because I think it is one of the most interesting things that is legislated , etc. How can something that is only yours , only touches you, only affects you be justifiably controlled, and what ``justification'' have colonial powers used. 
On the other side of this, I am equally interested in looking at how bodies are used as tools in resistance to colonialism. The Fall illustrated this well with the use of body as a shield, and in the documentary with the women clashing with the police with their bodies uncovered.

\paragraph{}
From OED we can see it etymologically germanic, with roots most likely from the old german \textit{botah}. Also mentioned is a connection to the latin \textit{Corpus} especially the idea of a body as a collection i.e \textit{corpus christi} (the collection of writing on christ)
\paragraph{Various Definitions from OED}
\begin{itemize}
\item ``The physical or mortal nature, state, or aspect of man. Frequently in in (the) body, out of (the) body and variants, sometimes contrasted with in spirit.''

\item``The complete physical form of a person or animal; the assemblage of parts, organs, and tissues that constitutes the whole material organism.''

\item``A united or organized whole; an aggregate of individuals characterized by some common attribute; a collective mass.''

\item``Substance, as opposed to representation, shadow, etc.; reality.''

\end{itemize}
Looking at these definitions, all of them will be very interesting to interrogate as this term continues. Already I feel like I could look at the fall with the definition of collective mass, I am also very interested in contrasting the body with the spirit and will be looking for that in our readings.
