

\paragraph{}

Going from the OED of ``A united or organized whole; an aggregate of individuals characterized
by some common attribute; a collective mass'' I want to look at Animals People as conflict between two bodies, the Kampani and the ``organized whole'' of the Zafar, Farouq, and all of Animals people. 
We can see Farouq as ``Zafar’s right hand man''. This turn of phrase usually just signifies closeness (literally being on his right , so close he is touching his hand) but as a ( unfortunately, in recent political climates) fan of combat sports. I take this to mean he also acts as Zafar's literal right hand. One of his 8 (9 if we are talking about Lethwei\footnote{Lethwei is a martial art that allows headbutts. \url{https://www.lawrentian.com/archives/1018119}})  - weapons. Before looking more at analogy that I have perhaps already given up, Zafar is most likely the head of the aggregated individuals, but through the lens of combat, Zafar's hunger strike would run counter to that - since to lose your `head' or consciousness  is to lose the fight -- near unilaterally. Thus why I brought up Lethwei, since we must jive the use of the head as the weapon, or equally likely, it is simply wrong to assume the aggregate of individuals as being ``headed'' especially since in not doing so this contrasts them even further from the Kampani.

Meanwhile the Kampani, the corporation responsible, is surely a body, but perhaps one more like the ``Khã-in-the-Jar'', which is even said here ``the Chairman of the Board, alias my little two-headed friend. His advice proves that he too is a selfish cunt and that everyone in this world is out for number one. “This is good,” says he, “when Elli doctress is in Amrika, it will give you a chance to get us out of here.” Some days later he informs me he has told the other members of the Board, they’ve passed a resolution welcoming the merger between Somraj and Elli'' 

This creates an interesting question of not how this fight would play out. A body that is 2 heads on a foetal corpse pitted against a body with a ``constant muscular tonus'' and no true head.(16) When put like there is no question. The classic analogy of david vs goliath is inverted here, with the weaker `fighter' being the Kampani while the goliath of Animals people wait. It's ``they’ll fight if they are forced to come to the court'' so much of the book focuses on this question of will the fight happen - not what will the outcome of the fight be. 
